\textsf{Are large language models superhuman chemists?}

### 2024-10-17 src/tex/ms.tex
Update src/tex/ms.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>

To understand whether the capabilities of the leading models align with the preferences of professional chemists, we selected 1000 data points from the original dataset to create a meaningful evaluation set, where molecules are represented as SMILES.
We only considered molecules for which we could obtain IUAPC names to ablate the effect of different molecular representations.

>>>>

To understand whether the capabilities of the leading models align with the preferences of professional chemists, we randomly selected 1000 data points from the original dataset to create a meaningful evaluation set, where molecules are represented as SMILES.
To ablate the effect of different molecular representations, we only considered questions for which we could obtain IUPAC names for both molecules present.
